An exploratory analysis of the influence of resource use on the yield verse quality trade-off in Australian vineyards

### 2023-07-25 article.tex
looking at final results section.

% A map and a table just like the t-test section.

@@

The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.

\subsubsection{Model Comparisons: Productivity Verse Value}
% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
%
% There were two subsets - when comparing these models what is the difference between them?
%
Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.

@@

\subsection{Model Validation}
To validate the performance of these models k-fold cross validation was used. This was done using 10 folds, $k=10$, repeated 100 times. The models performed similarly to their original counter parts (see Table \ref*{tab:kfold}).
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \begin{tabular}{cccc}
          & RMSE      & R2        & MAE       \\
  Model 1 & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
  Model 2 & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
  Model 3 & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
  Model 4 & 2.235E-01 & 9.500E-01 & 1.279E-01
  \end{tabular}
  \end{table}
\section{Discussion}
\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, (see Figures 1 and 2) and underestimating crop value in models 3 and 4 (see Figures 3 and 4).
% this needs serious revision.
This study investigated the general relationships between input resources of a vineyard, including fuel and water, and the outputs including yield and value. Some regions appeared to produce many low quality grapes at scale compared to attempting to produce fewer higher quality grapes. This behaviour can be observed when reviewing Wine Australia’s annual reports, where it is apparent that warm inland regions such as the Riverland are known to only produce large amounts of lower graded grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, regions such as Tasmania only produce A grade grapes but in much smaller quantities than the Riverland. Knowing that the difference in pricing per tonne can exceed a magnitude of 10 between grades E and A, the operations in regions that target different grades would have varied priorities. However, some regions such as the Yarra Valley produce a Variety of different grades of grapes, from C to A, highlighting that vineyard priorities, although may be somewhat present within regional classifications, are not necessarily aligned within a given region.

>>>>

@@

% What are you trying to say here?
% We want to compare how much influence each variable has on the model!
% This is prior to postulating about the why these variables matter, or have so much influence.
% A table will help to compare the continuous variables, the others are done in the violin plot.
% What is this below paragraph?
The correlation between average sales price and yield was a negative trend (see table 2); the contributing factors to yield and average sales price was ???. Correlation values showed that water and emissions increased with yield but decreased with average sale price (see Table 4).
In alternative attempts at models it was found that without the incorporation of GI Region or year the predictions greatly under performed. The possible reason behind this effect was that different strategies are likely employed between different regions, where some regions target the mass production of cheaper grapes over quality. % ALSO THAT CATASTROPHES HAPPEN EVEN ON SMALL SCALES THis needs to be tied up better.
\subsubsection{Model Comparisons: Productivity Verse Value}
% wHY ARE WE COMPARING MODELS?
% We compare models to see which predictors contributed relatively to each of the models.
% There were two subsets - when comparing these models what is the difference between them?
Models were compared using $R^2$ values. The comparison of models performance showed that the average price per tonne of grapes describes a great deal of the relationship between predictor and response when comparing Model 2 to Model 4 
% Graph of productivity verse value.

@@

\subsection{Model Validation}
To validate the performance of these models k-fold cross validation was used. This was done using 10 folds, $k=10$, repeated 100 times. The models performed similarly to their original counter parts (see Table \ref*{tab:kfold}).
\begin{table}[]
  \label{tab:kfold}
  \caption{Model validation using k-fold cross validation, for 10 folds repeated 100 times.}
  \begin{tabular}{cccc}
          & RMSE      & R2        & MAE       \\
  Model 1 & 3.087E-01 & 9.045E-01 & 2.165E-01 \\
  Model 2 & 5.104E-01 & 7.409E-01 & 3.493E-01 \\
  Model 3 & 1.652E-01 & 9.723E-01 & 1.008E-01 \\
  Model 4 & 2.235E-01 & 9.500E-01 & 1.279E-01
  \end{tabular}
  \end{table}
\section{Discussion}
\subsection{Limitations}
Limitations included overestimating yield for models 1 and 2, (see Figures 1 and 2) and underestimating crop value in models 3 and 4 (see Figures 3 and 4).
% this needs serious revision.
This study investigated the general relationships between input resources of a vineyard, including fuel and water, and the outputs including yield and value. Some regions appeared to produce many low quality grapes at scale compared to attempting to produce fewer higher quality grapes. This behaviour can be observed when reviewing Wine Australia's annual reports, where it is apparent that warm inland regions such as the Riverland are known to only produce large amounts of lower graded grapes \cite{wineaustraliaNationalVintageReport2022,winemakersfederationofaustraliaNationalVintageReport2017}. Comparatively, regions such as Tasmania only produce A grade grapes but in much smaller quantities than the Riverland. Knowing that the difference in pricing per tonne can exceed a magnitude of 10 between grades E and A, the operations in regions that target different grades would have varied priorities. However, some regions such as the Yarra Valley produce a Variety of different grades of grapes, from C to A, highlighting that vineyard priorities, although may be somewhat present within regional classifications, are not necessarily aligned within a given region.
